\cvsection{Experience}
\begin{cventries}
  \cventry
    {Science Archive Working Group Core Member, SKA Regional Centre Steering Committee (SRCSC)}
    {University of Manchester}
    {Manchester, UK}
    {February 2021 - present}
    {
      \begin{cvitems}
        \item {Core Member of SRCSC Working Group 4 (WG4): SW, Science Archive-VO-FAIR.}
        \item{WG4 will define the requirements for the Square Kilometre Array (SKA) Science Archive that will drive the design and define the policies and rules to make the Science Archive conform to FAIR principles and interoperate within the IVOA ecosystem.}
      \end{cvitems}
    }\vspace{-15pt}

  \cventry
    {Research Software Community Manager, Software Sustainability Institute (SSI)}
    {}
    {}
    {September 2019 - present}
    {
      \begin{cvitems}
        \item {Project Manager for the SSI Fellowship Programme and Collaborations Workshop.}
        \item{Product Owner for the Fellows management software lowFAT}
      \end{cvitems}
    }\vspace{-15pt}

  \cventry
    {Research Associate, Jodrell Bank Centre for Astrophysics (JBCA)}
    {}
    {}
    {June 2017 - August 2019}
    {
      \begin{cvitems}
        \item {Leading a project to store, process and analyse $e$MERLIN data on the Cloud through integration of containers, open notebooks and open source software to facilitate transparency and reproducibility for radio astronomy workflows (\url{https://github.com/rainsworth/eMERLIN-IRIS}).}
        \item {Core Contributor for the Alan Turing Institute's project The Turing Way (PI Dr. Kirstie Whitaker) to develop a handbook for reproducible data science (\url{https://github.com/alan-turing-institute/the-turing-way}).}
        \item {Member of the H2020 RadioNET RINGS project working to develop an algorithm for calibrating dispersive delay corrections in long baseline interferometry, for low frequency radio telescopes such as LOFAR.}
        \item {Interferometry Centre for Excellence (ICE) Open Science Champion to advocate, train colleagues, give presentations and organise events relating to Open Science in Astronomy, and engage in cross-stakeholder conversations.}
        \item {Disseminating research insights through invited seminars, talks at international conferences, interviews and public outreach.}
      \end{cvitems}
    }\vspace{-6pt}

\cventry
    {Postdoctoral Research Fellow}
    {Dublin Institute for Advanced Studies (DIAS)}
    {Dublin, Ireland}
    {October 2014 - October 2016}
    {
      \begin{cvitems}
        \item{Impact: Our team was the first to successfully detect and model the properties of a young star with the International Low-Frequency Array (LOFAR) Telescope using the facilities at the Irish Centre for High End Computing (ICHEC).}        
        \item {I pioneered the collection, cleaning, analysis/statistical modelling and visualisation of radio data for young stars at previously unexplored wavelengths (\url{https://github.com/rainsworth/GMRT-TAU_catalogue}).}
        \item {Part of a worldwide collaboration to develop novel processing and analytical techniques for terabytes of data from LOFAR.}
        \item {Member of the Communications Working Group to re-define the public communication strategy of DIAS through restructure of the website and social media developments.}
      \end{cvitems}
    }\vspace{-15pt}

  \cventry
    {Ph.D. Student; Supervisors: Prof. Tom Ray (DIAS), Prof.. Anna Scaife (JBCA)}
    {}
    {}
    {November 2010 - September 2014}
    {
      \begin{cvitems}
        \item {Led three projects performing systematic modelling of multi-wavelength, multi-scale datasets of protostellar jets from AMI, $e$MERLIN \& GMRT to disentangle competing radiation processes and investigate the jet launching mechanism.}
        \item {Involved in the commissioning of $e$MERLIN, which included the reduction and analysis of legacy data (Thermal Jets, PEBBLeS) intermediate to the original MERLIN and the fully upgraded $e$MERLIN.}
        \item {Published the first investigations of YSOs at metre wavelengths and pioneered to characterise this very long wavelength emission through follow-up observing campaigns on the GMRT and LOFAR.}
      \end{cvitems} 
    }\vspace{-6pt}

\cventry
    {Lab Manager - Office of Information Technology}
    {University of Tennessee (UT)}
    {Knoxville, TN, USA}
    {January 2009 - August 2010}
    {
      \begin{cvitems}
        \item {Managed and trained student assistants; maintained the condition of the equipment and physical area in all labs; oversaw staffing of the computer labs; troubleshoot problems with computer lab equipment; and enforced departmental and university policy.}
      \end{cvitems}
    }\vspace{-15pt}

\cventry
    {Summer Research Fellow; Supervisor: Prof. Michael Guidry (UT)}
    {}
    {}
    {May 2009 - August 2009}
    {
      \begin{cvitems}
        \item {Studied the explosion mechanism of Type Ia Supernovae through computational simulations using the FLASH code on the supercomputing facilities at Oak Ridge National Laboratory.}
      \end{cvitems}
    }\vspace{-15pt}

\cventry
    {Student Assistant - Office of Information Technology}
    {}
    {}
    {February 2006 - January 2009}
    {
      \begin{cvitems}
        \item {Maintained appropriate computer lab access, collected required information and secured lab resources; provided assistance to users with system errors, hardware recovery and software consulting where possible; and assisted instructors by setting up special requests for lab classes.}
      \end{cvitems}
    }\vspace{-15pt}

\cventry
    {Undergraduate Student Researcher; Supervisor: Prof. Michael Guidry (UT)}
    {}
    {}
    {June 2008 - August 2008}
    {
      \begin{cvitems}
        \item {Studied the interactions between colliding galaxies using computational simulations developed by the UT Astrophysics Group.}
      \end{cvitems}
    }\vspace{-6pt}

\cventry
    {Undergraduate Student Research Program Intern; Supervisor: Dr. Raghvendra Sahai (JPL/Caltech)}
    {NASA Jet Propulsion Laboratory / California Institute of Technology (JPL/Caltech)}
    {Pasadena, CA, USA}
    {September 2008 - December 2008}
    {
      \begin{cvitems}
        \item {Developed and applied a procedure for the reduction and calibration of near-infrared echelle spectroscopic data for (a)  a sample of pre-planetary nebulae to look for the signatures of high-velocity outflows that shape the resulting planetary nebula, and (b) stellar interlopers: young stars with winds speeding through and interacting with dense interstellar clouds.}
      \end{cvitems}
    }
\end{cventries}
