\cvsection{Publications}
\cvsubsection{Refereed}
\begin{cvpubs}
  \cvpub
    {
      \begin{cvetar}
      \item{A. Feeney-Johansson, S. J. D. Purser, T. P. Ray,  J. Eisl{\"o}ffel, M. H{\"o}ft, A. Drabent and \textbf{R. E. Ainsworth}, ``The First Detection of a Low-frequency Turnover in Nonthermal Emission from the Jet of a Young Star'', \textit{Astrophysical Journal Letters}, 855, L7, 2019. \url{https://doi.org/10.3847/2041-8213/ab4b56}}
       \item {S. J. D. Purser, \textbf{R. E. Ainsworth}, T. P. Ray, D. A. Green, A. M. Taylor and A. M. M. Scaife, ``Constraining the nature of DG Tau A's thermal and non-thermal radio emission'', \textit{Monthly Notices of the Royal Astronomical Society}, 481, 5532--5542, 2018. \url{https://doi.org/10.1093/mnras/sty2649}}
        \item {C. P. Coughlan, \textbf{R. E. Ainsworth}, J. Eisl{\"o}ffel, M. H{\"o}ft, A. Drabent, A. M. M. Scaife, T. P. Ray, et~al., ``A LOFAR Detection of the Low Mass Young Star T~Tau at 149\,MHz'', \textit{Astrophysical Journal}, 834, 206--213, 2017. \url{https://doi.org/10.3847/1538-4357/834/2/206}}
        \item {\textbf{R. E. Ainsworth}, C. P. Coughlan, D. A. Green, A. M. M. Scaife and T. P. Ray, ``A GMRT survey of regions towards the Taurus molecular cloud at 323 and 608\,MHz'', \textit{Monthly Notices of the Royal Astronomical Society}, 462, 2904--2917, 2016. \url{https://doi.org/10.1093/mnras/stw1847}}
        \item {\textbf{R. E. Ainsworth}, A. M. M. Scaife, D. A. Green, C. P. Coughlan and T. P. Ray, ``GMRT detections of low mass young stars at 323 and 608\,MHz'', \textit{Monthly Notices of the Royal Astronomical Society}, 459, 1248--1258, 2016. \url{https://doi.org/10.1093/mnras/stw708}}
        \item {\textbf{R. E. Ainsworth}, A. M. M. Scaife, T. P. Ray, A. M. Taylor, D. A. Green and J. V. Buckle, ``Tentative evidence for relativistic electrons generated by the jet of the young Sun-like star DG~Tau'', \textit{Astrophysical Journal}, 792, L18, 2014. \url{https://doi.org/10.1088/2041-8205/792/1/l18}}
        \item {\textbf{R. E. Ainsworth}, T. P. Ray, A. M. M. Scaife, J. S. Greaves and R. J. Beswick, ``Sub--arcsecond high sensitivity measurements of the DG Tau jet with e--MERLIN", \textit{Monthly Notices of the Royal Astronomical Society}, 436, L64--L68, 2013. \url{https://doi.org/10.1093/mnrasl/slt114}}
        \item {\textbf{R. E. Ainsworth}, A. M. M. Scaife, T. P. Ray, et al., ``AMI radio continuum observations of young stellar objects with known outflows", \textit{Monthly Notices of the Royal Astronomical Society}, 423, 1089--1108, 2012. \url{https://doi.org/10.1111/j.1365-2966.2012.20935.x}}
        \item {A. M. M. Scaife, J. Hatchell, \textbf{R. E. Ainsworth}, et al., ``AMI--LA radio continuum observations of Spitzer c2d small clouds and cores: Serpens region", \textit{Monthly Notices of the Royal Astronomical Society}, 420, 1019--1033, 2012. \url{https://doi.org/10.1111/j.1365-2966.2011.19957.x}}
        \item {A. M. M. Scaife, J. V. Buckle, \textbf{R. E. Ainsworth}, et al., ``Radio continuum observations of Class I protostellar disks in Taurus: constraining the greybody tail at centimetre wavelengths", \textit{Monthly Notices of the Royal Astronomical Society}, 420, 3334--3343, 2012. \url{https://doi.org/10.1111/j.1365-2966.2011.20254.x}}
      \end{cvetar}
    }
\end{cvpubs}

\cvsubsection{Unrefereed}
\begin{cvpubs}
  \cvpub
    {
      \begin{cvetar}
        \item {L. Woodley, C. Pratt, S. Kobilka and \textbf{R. E. Ainsworth}, ``CSCCE Community Profile: Software Sustainability Institute Research Software Community'', Zenodo, July 20, 2021. \url{https://doi.org/10.5281/zenodo.4947235}}
        \item {L. Woodley, C. Pratt, \textbf{R. E. Ainsworth}, et al., ``Using virtual events to facilitate community building: curated resources'', Zenodo, November 12, 2020. \url{https://doi.org/10.5281/zenodo.4270105}}
        \item {L. Woodley, C. Pratt, \textbf{R. E. Ainsworth}, et al., ``Using virtual events to facilitate community building: event formats'', Zenodo, July 17, 2020. \url{https://doi.org/10.5281/zenodo.3934385}}
        \item {S. Sufi, A. Nenadic, \textbf{R. E. Ainsworth}, et al., ``Guidance for running online training'', Zenodo, June 30, 2020. \url{https://doi.org/10.5281/zenodo.3923948}}
        \item {\textbf{R. E. Ainsworth}, A. M. M. Scaife, T. P. Ray, D. A. Green and J. V. Buckle, ``The Lowest Frequency Observations of YSOs with the GMRT'', Protostars and Planets VI, Heidelberg, July 15-20, 2013. Poster \#1H019.}
        \item {R. Sahai, M. Claussen, M. Morris and \textbf{R. E. Ainsworth}, ``Ballistic Stellar Interlopers producing Bow-Shocks in the Interstellar Medium'', American Astronomical Society Meeting \#213, \textit{Bulletin of the American Astronomical Society}, 41, 465, 2009.}
      \end{cvetar}
    }
\end{cvpubs}

\cvsubsection{Press Releases}
\begin{cvpubs}
  \cvpub
    {
      \begin{cvetar}
        \item {R. Sahai, M. Morris, M. Claussen and \textbf{R. E. Ainsworth}, ``Hubble Finds Stars That `Go Ballistic' '', NASA Jet Propulsion Laboratory, 7 January 2009. \url{https://www.jpl.nasa.gov/news/news.php?release=2009-002}}
      \end{cvetar}
    }    

\end{cvpubs}

